---
title: R Plot Gallery
author: R package build
date: '2021-10-24'
slug: test-hide-code
categories: []
tags: []
subtitle: ''
summary: 'In this post, I have listed plenty of plots generated by R. I hope you enjoy this gallery!'
authors: []
lastmod: '2021-10-24T17:35:12+01:00'
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: yes
projects: []
# output:
#   html_document:
#     theme: flatly
#     highlight: tango
---
<script>
function myFunction(x) {
  if (x.style.display === "none") {
    x.style.display = "block";
  } else {
    x.style.display = "none";
  }
}
</script>
<style scoped>
.cb{
    background-color: white;
    color: #555555;
    border-radius:12px;
    outline: none;
    transition-duration: 0.4s;
}
.cb:focus {
  outline: none;
}
.cb:hover{
background-color: #555555;
color: white;
}
</style>
```{r echo=FALSE, message=FALSE, results='hide', warning=FALSE}
# import data

library(tidyverse)
library(tidymodels)
library(readr)
library(scales)
library(janitor)
library(tidytuesdayR) 
library(cytools)
theme_set(theme_light())

pumpkins_raw <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-10-19/pumpkins.csv")

water_raw <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-05-04/water.csv")

pumpkins <-
  pumpkins_raw %>%
  separate(id, into = c("year", "type")) %>%
  mutate(across(c(year, weight_lbs, ott, place), parse_number)) %>%
  filter(type == "P") %>%
  select(weight_lbs, year, place, ott, gpc_site, country)
```

**Note:** Don't be fooled by the subtitle that tells you this article is a 1 min read. 

In this post, I have listed plenty of plots generated by R. You can enjoy these plots as much as you like. If you are interested in how to reproduce these plots, please click on the `Code` button below the plots. If you are interested in what these plots can tell you, please click on the `Explanation` button next to `Code`. I hope you enjoy this gallery!

<figure style="padding: 0rem; margin: 0rem 0rem">
```{r echo=FALSE}
pumpkins %>%
  filter(ott > 20, ott < 1e3) %>%
  ggplot(aes(ott, weight_lbs, color = place)) +
  geom_point(alpha = 0.2, size = 1.1) +
  labs(x = "over-the-top inches", y = "weight (lbs)") +
  scale_color_viridis_c()
```
<button class="cb" onclick="myFunction(myDIV1)">Code</button>
<div id="myDIV1" style="display: none">
```{r eval=FALSE}
pumpkins %>%
  filter(ott > 20, ott < 1e3) %>%
  ggplot(aes(ott, weight_lbs, color = place)) +
  geom_point(alpha = 0.2, size = 1.1) +
  labs(x = "over-the-top inches", y = "weight (lbs)") +
  scale_color_viridis_c()
```
</div>
<button class="cb" onclick="myFunction(JAcl5tRJVM)">Explanation</button>
<div id="JAcl5tRJVM" style="display: none">

</div>
</figure> 

<figure style="padding: 0rem; margin: 0rem 0rem">
```{r echo=FALSE}
pumpkins %>%
  filter(ott > 20, ott < 1e3) %>%
  ggplot(aes(ott, weight_lbs)) +
  geom_point(alpha = 0.2, size = 1.1, color = "gray60") +
  geom_smooth(aes(color = factor(year)),
    method = lm, formula = y ~ splines::bs(x, 3),
    se = FALSE, size = 1.5, alpha = 0.6
  ) +
  labs(x = "over-the-top inches", y = "weight (lbs)", color = NULL) +
  scale_color_viridis_d()
```
<button class="cb" onclick="myFunction(myDIV2)">Code</button>
<div id="myDIV2" style="display: none">
```{r eval=FALSE}
pumpkins %>%
  filter(ott > 20, ott < 1e3) %>%
  ggplot(aes(ott, weight_lbs)) +
  geom_point(alpha = 0.2, size = 1.1, color = "gray60") +
  geom_smooth(aes(color = factor(year)),
    method = lm, formula = y ~ splines::bs(x, 3),
    se = FALSE, size = 1.5, alpha = 0.6
  ) +
  labs(x = "over-the-top inches", y = "weight (lbs)", color = NULL) +
  scale_color_viridis_d()
```
</div>
<button class="cb" onclick="myFunction(O5FeVvKch2)">Explanation</button>
<div id="O5FeVvKch2" style="display: none">

</div>
</figure> 

<figure style="padding: 0rem; margin: 0rem 0rem">
```{r echo=FALSE}
pumpkins %>%
  mutate(
    country = fct_lump(country, n = 10),
    country = fct_reorder(country, weight_lbs)
  ) %>%
  ggplot(aes(country, weight_lbs, color = country)) +
  geom_boxplot(outlier.colour = NA) +
  geom_jitter(alpha = 0.1, width = 0.15) +
  labs(x = NULL, y = "weight (lbs)") +
  theme(legend.position = "none")
```
<button class="cb" onclick="myFunction(myDIV3)">Code</button>
<div id="myDIV3" style="display: none">
```{r eval=FALSE}
pumpkins %>%
  mutate(
    country = fct_lump(country, n = 10),
    country = fct_reorder(country, weight_lbs)
  ) %>%
  ggplot(aes(country, weight_lbs, color = country)) +
  geom_boxplot(outlier.colour = NA) +
  geom_jitter(alpha = 0.1, width = 0.15) +
  labs(x = NULL, y = "weight (lbs)") +
  theme(legend.position = "none")
```
</div>
<button class="cb" onclick="myFunction(explain3)">Explanation</button>
<div id="explain3" style="display: none">
dafsafdafdafda
</div>
</figure> 

<figure style="padding: 0rem; margin: 0rem 0rem">
```{r echo=FALSE}
water_raw %>%
  filter(
    country_name == "Sierra Leone",
    lat_deg > 0, lat_deg < 15, lon_deg < 0,
    status_id %in% c("y", "n")
  ) %>%
  ggplot(aes(lon_deg, lat_deg, color = status_id)) +
  geom_point(alpha = 0.1) +
  coord_fixed() +
  guides(color = guide_legend(override.aes = list(alpha = 1)))
```
<button class="cb" onclick="myFunction(AfH2K7Wc0h)">Code</button>
<div id="AfH2K7Wc0h" style="display: none">
```{r eval=FALSE}
water_raw %>%
  filter(
    country_name == "Sierra Leone",
    lat_deg > 0, lat_deg < 15, lon_deg < 0,
    status_id %in% c("y", "n")
  ) %>%
  ggplot(aes(lon_deg, lat_deg, color = status_id)) +
  geom_point(alpha = 0.1) +
  coord_fixed() +
  guides(color = guide_legend(override.aes = list(alpha = 1)))
``` 
</div>
<button class="cb" onclick="myFunction(kaDimFIfN7)">Explanation</button>
<div id="kaDimFIfN7" style="display: none">

</div>
</figure>

<figure style="padding: 0rem; margin: 0rem 0rem">
```{r echo=FALSE, warning=FALSE, message=FALSE}
library(janitor)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(ggridges)

lincoln_weather %>% 
  clean_names() %>% 
  ggplot() + 
  geom_density_ridges_gradient(aes(x = `mean_temperature_f`, y = `month`, fill = ..x..),
                               scale = 3, rel_min_height = 0.01, alpha = 0.5) +
  stat_summary(aes(x=mean_temperature_f, y = month, group=1),
               geom = "line", alpha=0.6, fun=mean) +
  stat_summary(aes(x=mean_temperature_f, y = month, color="#24EA53"),
               geom = "point", alpha=0.6, fun=mean) +
  scale_fill_viridis(name = "Temp. [F]", option = "C") +
  scale_colour_discrete(guide = FALSE) +
  labs(title = 'Temperatures in Lincoln NE in 2016') +
  theme_ipsum() +
    theme(
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )
```
<button class="cb" onclick="myFunction(YfY4lyskfJ)">Code</button>
<div id="YfY4lyskfJ" style="display: none">
```{r eval=FALSE}
library(janitor)
library(tidyverse)
library(hrbrthemes)
library(viridis)
library(ggridges)

lincoln_weather %>% 
  clean_names() %>% 
  ggplot() + 
  geom_density_ridges_gradient(aes(x = `mean_temperature_f`, y = `month`, fill = ..x..),
                               scale = 3, rel_min_height = 0.01, alpha = 0.5) +
  stat_summary(aes(x=mean_temperature_f, y = month, group=1),
               geom = "line", alpha=0.6, fun=mean) +
  stat_summary(aes(x=mean_temperature_f, y = month, color="#24EA53"),
               geom = "point", alpha=0.6, fun=mean) +
  scale_fill_viridis(name = "Temp. [F]", option = "C") +
  scale_colour_discrete(guide = FALSE) +
  labs(title = 'Temperatures in Lincoln NE in 2016') +
  theme_ipsum() +
    theme(
      panel.spacing = unit(0.1, "lines"),
      strip.text.x = element_text(size = 8)
    )
``` 
</div>
<button class="cb" onclick="myFunction(yZMi3HtkXi)">Explanation</button>
<div id="yZMi3HtkXi" style="display: none">

</div>
</figure>
<br><br>
**To be continued...**
